High-Performance Data Analysis on Janus using Apache Spark

### 2013-12-17 paper.tex
minor changes to outline
added images directory
Finish introduction (?)

@@

\section{Evaluation}
% janus
    % overview
%%% DIRECTLY COPY-PASTED TEXT %%%
University of the University of Colorado's Top-
31 (June 2010) supercomputer system, Janus
    % specs (ref)
%%% DIRECTLY COPY-PASTED TEXT %%%
The final Janus computational
system consists of 1,368 nodes, each containing two six-
core Intel Xeon Westmere-EP chips at 2.8 GHz, for a total
of 2,736 processors and 16,416 cores with a theoretical
peak performance of 184 TFLOP/s. Each core has 2
GB of 1333 MHz DDR3 RAM for a total of 24 GB per
node and 32 TB of memory in the entire system. [REF]
% spark
    % reason for spark (diskless)
    % installation (default???)
    % version number (Spark 0.8.0, Scala 2.9.3)
% purpose of trials (speedup, efficiency, install on Janus)
    % find ideal configurations

@@

\subsection{Results}
% small grep test
    % serial run time (graph)
    % efficiency (graph)
    % karp flatt (graph)
% cores grep test
    % scale up, workers per node (graph)
% large grep test
    % serial run time (graph)
    % efficiency (graph)
% pagerank test 1
% pagerank test 2
% ...

>>>>

We can also see from this example a significant limitation of MapReduce: each
intermediate $(k, v)$ set is written to the distributed filesystem.  As such,
in order for MapReduce to be efficient, the individual tasks must be very
large.

However, some algorithms are not well-described by a simple map-and-then-reduce
pattern, and require multiple iterations.  If each iteration is small, the
algorithm's performance will be bottlenecked by this file I/O. For these
problems, another approach is needed.

Spark was designed at the UC Berkeley AMPLab to address these concerns using a
more flexible abstraction for distributed data \citep{zaharia}. Rather than
assuming that all intermediate data is stored on a filesystem, Spark uses
\emph{Resilient Distributed Datasets}, or RDDs, to represent data that is
stored on disk, cached in memory, or possibly has not been computed yet at all
\citep{zaharia_rdd}.  It is primarily targeted toward Scala, a statically-typed
functional language for the Java Virtual Machine.

@@

\section{Evaluation}
% janus
    % overview
%%% DIRECTLY COPY-PASTED TEXT %%%
University of the University of Colorado's Top-
31 (June 2010) supercomputer system, Janus
    % specs (ref)
%%% DIRECTLY COPY-PASTED TEXT %%%
The final Janus computational
system consists of 1,368 nodes, each containing two six-
core Intel Xeon Westmere-EP chips at 2.8 GHz, for a total
of 2,736 processors and 16,416 cores with a theoretical
peak performance of 184 TFLOP/s. Each core has 2
GB of 1333 MHz DDR3 RAM for a total of 24 GB per
node and 32 TB of memory in the entire system. (REF)
% spark
    % reason for spark (diskless)
    % installation (default???)
    % version number (Spark 0.8.0, Scala 2.9.3)
% purpose of trials (speedup, efficiency, install on Janus)
    % find ideal configurations

@@

\subsection{Results}
% small grep test
    % serial run time (graph)
    % efficiency (graph)
    % karp flatt (graph)
% cores grep test
    % scale up, workers per node (graph)
% large grep test
    % serial run time (graph)
% pagerank test 1
% pagerank test 2
% ...
